HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Wardlow final comments.

The starting point for the sample selection is source extraction and
photometry.  For the objects in this paper, individual catalogs were generated
for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
follow-up of a sensitivity and angular resolution that is comparable to our
ALMA data, so it is the best sample with which to compare our results.  The
significant overlap in $S_{870}$ between our sample and ALESS is evidence that
the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in
ALESS (recall Figure~\ref{fig:sample}, which shows that ALESS sources have much
lower $S_{500}$ than our targets).  This difference is likely due to
differences in dust temperature and/or redshift distributions of the two
samples and probably arises from selection effects.

@@

Finally, the brightest source in the {\it Herschel}-ALMA sample is
HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.
However, there are also two objects with multiple sources that have separations
smaller than 1$\arcsec$, which have summed flux densities comparable to this;
namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching
the values found in the most extreme systems, such as GN20
\citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm, Robson:2014xy}.  It is
a level that is extremely difficult to reproduce in simulations
\citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
multiple sources represent blends of physically unassociated systems.  Testing
this possibility requires redshift determinations of each source and is beyond
the scope of this paper.

>>>>

The starting point for the sample selection is source extraction and
photometry.  For the objects in this paper, individual catalogs were generated
for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $< 2 ^\circ$ and totaling $55\,$deg$^2$.

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
follow-up of a sensitivity and angular resolution that is comparable to our
ALMA data, so it is the best sample with which to compare our results.  The
significant overlap in $S_{870}$ between our sample and ALESS is evidence that
the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios (even when the
effect of lensing in our sample is taken into account) than the DSFGs in ALESS
(recall Figure~\ref{fig:sample}, which shows that ALESS sources have much lower
$S_{500}$ than our targets).  This difference is likely due to differences in
dust temperature and/or redshift distributions of the two samples and probably
arises from selection effects.

@@

Finally, the brightest source in the {\it Herschel}-ALMA sample is HADFS11.0,
with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.  However,
there are also two objects with multiple sources that have separations smaller
than 1$\arcsec$, which have summed flux densities comparable to this; namely
HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching the
values found in the most extreme systems, such as GN20
\citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm, Robson:2014xy}.  It is
a level that is extremely difficult to reproduce in simulations
\citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
multiple sources represent blends of physically unassociated systems.  We
explore this possibility via comparison to theoretical models in
Section~\ref{sec:spatialdist}, but a direct empirical test requires redshift
determinations of each source and is beyond the scope of this paper.
